%
%Academic CV LaTeX Template
% Author: Dubasi Pavan Kumar
% LinkedIn: https://www.linkedin.com/in/im-pavankumar/
% License: MIT
%
% For errors, suggestions, or improvements, please contact:
% Email: pavankumard.pg19.ma@nitp.ac.in
%

\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
%\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like (similar to Arial/Calibri)
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont} % Times-like (similar to Times New Roman)
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont} % Bookman (readable serif)
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont} % Avant Garde-like (similar to Trebuchet MS)
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont} % Computer Modern Sans Serif
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont} % Quasi-Helvetica (another Arial/Calibri alternative)
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont} % Quasi-Palatino (another elegant serif option)
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont} % Quasi-Times (another Times New Roman alternative)
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont} % Charter (clean serif font)

\begin{document}
\headerfontiii

% Header
\begin{center}
    {\Huge\textbf{NGUYEN THANH TUNG}}
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
     \faPhone\ +84869 647 600  | 
     \faEnvelope\ \href{mailto:tung.nguyenfrom108bku@hcmut.edu.vn}{tung.nguyenfrom108bku@hcmut.edu.vn} |
     \socialicon{\faLinkedin} \href{https://www.linkedin.com/in/thanh-tùng-nguyễn-30a130334/}{Thanh-Tung} | 
     \socialicon{\faGithub} \href{https://github.com/thanhtunglk1}{Thanh-Tung} 
     %\href{https://www.yourwebsite.com/}{yourwebsite.com}
    }
\end{center}
\vspace{-6mm}

\begin{center}
    \small{Thu Duc, Ho Chi Minh}
\end{center}

\vspace{-4mm}

\section{\textbf{Objective}}
\vspace{1mm}
\small{
Fourth-year Electronics and Telecommunications student with a strong interest in Digital Design. Possesses hands-on experience in digital logic design, FPGA implementation, and system-level verification through academic projects. Seeking an internship opportunity to apply digital design principles and gain practical experience in real-world engineering environments.
}
\vspace{-2mm}

\section{\textbf{Education}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
{Ho Chi Minh City University of Technology (HCMUT), VNU-HCM}{ }
{Major: Bachelor of Electronics - Telecommunications Engineering}{Oct 2022 - present}
\resumeItemListStart
\item \href{https://github.com/thanhtunglk1/My-Academy-CV-Transript/blob/master/Nguyen_Thanh_Tung_student_transcrip.pdf}{GPA: 3.1/4.0}
\item \textbf{Project 1:} RISC-V–Based SoC Design with System Bus and Peripherals Integration.
\item \textbf{Project 2:} FPGA-Based Multi-Band Audio Equalizer Using Folded FIR Architecture.
\item \textbf{Course:} Marvell “IC Design for AI Infrastructure” Training Course.
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-6mm}


\section{\textbf{Projects}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
  {Project 1: RISC-V–Based SoC Design with System Bus and Peripherals Integration.}
  {Tools: Cadence Xcelium/SimVision, Quartus II 13.0 sp1, ModelSim.}
  {April 2025}{}
  %{{}[\href{https://github.com/your-username/project-a}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item Designed and implemented a 5-stage pipelined RISC-V (RV32I) processor (IF, ID, EX, MEM, WB) with data forwarding and hazard handling.
  \item Implemented branch prediction schemes: static (always-taken/not-taken) and dynamic (2-bit saturating counter, global/local predictors).
  \item Integrated TileLink-UL/APB bus with a custom bridge to interface peripherals: SRAM (IS61LV25616), UART, LCD1602, 7-seg LED, watchdog timer.
  \item Verified functionality using directed testbenches, synthesized and deployed on Altera DE2-115 FPGA. 
\resumeItemListEnd

\resumeProject
{Project 2: FPGA-Based Multi-Band Audio Equalizer Using Folded FIR Architecture}
{Tools: MATLAB 2025a, Cadence Xcelium/SimVision, Quartus Prime 24.1 and QuestaSim.}
{November 2025}{}
%{{}[\href{https://github.com/your-username/project-b}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
\item Designed a multi-band audio equalizer using folded FIR filters, including low-pass, band-pass and high-pass filters.
\item Generated FIR coefficients in MATLAB using the Hamming window method at a 48 kHz sampling rate.
\item Verified filter performance using multi-tone sine inputs and FFT spectrum analysis in MATLAB.
\item Implemented the design on Altera DE10-Standard FPGA and interfaced with WM8731 audio codec (ADC/DAC), validated using an oscilloscope.
\resumeItemListEnd

\resumeProject
{Other Project:}
{Tools: MATLAB 2025a, Cadence Xcelium/SimVision/Genus/Virtuoso, Quartus Prime 24.1 and QuestaSim.}
{2024 - 2025}{}
%{{}[\href{https://github.com/your-username/project-b}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
\item Designed \& implemented multi-waveform generator (sine, square, triangle, sawtooth, ECG, noise) on DE10 Standard FPGA; verified via oscilloscope.
\item Designed \& implemented a single-precision floating-point adder/subtractor compliant with IEEE 754.
\item Verification of single-precision floating-point 8-Point Radix-2 FFT Core.
\item Designed CMOS logic gates and combinational circuits in FreePDK45, including full adders and decoders, with DRC/LVS-clean layouts.
\item Analyzed 6T SRAM cell and 8×8 SRAM array with decoder and sense amplifier; verified read/write stability and timing through circuit-level simulation.
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{\textbf{Technical Skills}}
\vspace{-0.4mm}
 \resumeHeadingSkillStart
  \resumeSubItem{HDL:}
    { Verilog and SystemVerilog}
  \resumeSubItem{Computer Architecture:}
  	{ RISC-V, Pipeline, Branch Prediction, Bus Protocols}
  \resumeSubItem{FPGA:}
  	{ Quartus, ModelSim/QuestaSim, DE2-115, DE10-Standard}
  \resumeSubItem{EDA Tools:}
    { Cadence Xcelium, Virtuoso, Genus, MATLAB, WaveDrom}
  \resumeSubItem{Programming Language:}
    { C, Assembly (AVR, RV32I), Bash, Makefile}
  \resumeSubItem{OS \& Documentation:}
    { Experienced with Linux (Ubuntu, CentOS), \LaTeX}

 \resumeHeadingSkillEnd
 
\section{\textbf{Language}}
\vspace{-0.4mm}
\resumeItemListStart
\item ENGLISH: TOEIC L/R 620
\resumeItemListEnd

\end{document}